Simulation Figures for Genome Biology (simulations)

### 2018-06-11 manuscript_figures/manuscript_figures_sims.Rmd
Try adding SE bars to simulation summary plots

```{r, fig.width = 8, fig.height = 5}
dplyr::filter(res_nullset, key == "rejectprop") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    facet_grid(. ~ dist) +
    scale_color_manual(values = col, guide = FALSE) +
    scale_y_continuous("Average % Rejected Tests", breaks = seq(0, 1, .01), labels = scales::percent) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Rejected proportion of in null simulations (average over 100 replications)") 
```

@@

```{r, fig.width = 8, fig.height = 5}
gp <- dplyr::filter(res_nullset, key == "TNR") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    facet_grid(. ~ dist) +
    scale_y_continuous("TPR", labels = scales::percent) +
    scale_color_manual(values = col, guide = FALSE) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Average TNR (over 100 replications)") 
gp

@@

## looking at noninformative vs. informative (cubic)
dplyr::select(res_covset, Method, setting, dist, key, mean_value) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("TPR"),
                  ! Method %in% c("ashq", "bonf")) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, color = Method)) +
    geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 1, scales = "free", labeller = labeller(dist = label_parsed)) +
    scale_x_continuous(labels = scales::percent) + 
    scale_y_continuous(labels = scales::percent) + 
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    ggtitle("Mean TPR for Informative and Noninformative Simulations") 
```

@@

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(pfdr + guides(color = FALSE, linetype = FALSE), ptpr, , rel_widths = c(1, 1.4), labels = LETTERS[1:2])
gp

@@

pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Null Proportion")

ptpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average TPR Across Varying Null Proportion")
```

@@

uniplot <- dplyr::select(res_unimodal, Method, dist, signal, key, mean_value, col, lty) %>%
    dplyr::filter(key %in% c("FDR", "TPR")) %>%
    tidyr::spread(key, mean_value) %>%
    ggplot(aes(x = TPR, y = FDR, color = Method)) +
    geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("TPR", labels = scales::percent, breaks = seq(0, 1, .2)) + 
    scale_y_continuous("FDR", labels = scales::percent, breaks = seq(0, 1, .2)) + 
    facet_grid(signal ~ dist, labeller = labeller(dist = label_parsed)) + 
    ggtitle("Average FDR and TPR Across Unimodal Settings")
uniplot

@@

pfdr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Informativeness")
pfdr

ptpr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ ., scales = "free_y") + expand_limits(y = 0) +
    ggtitle("Average TPR Across Varying Informativeness")
ptpr
```

>>>>

```{r, fig.width = 8, fig.height = 5}
dplyr::filter(res_nullset, key == "rejectprop") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se)) + 
    facet_grid(. ~ dist) +
    scale_color_manual(values = col, guide = FALSE) +
    scale_y_continuous("Average % Rejected Tests", breaks = seq(0, 1, .01), labels = scales::percent) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Rejected proportion in null simulations (average over 100 replications)") 
```

@@

```{r, fig.width = 8, fig.height = 5}
gp <- dplyr::filter(res_nullset, key == "TNR") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se)) + 
    facet_grid(. ~ dist) +
    scale_y_continuous("TPR", labels = scales::percent) +
    scale_color_manual(values = col, guide = FALSE) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Average TNR (over 100 replications)") 
gp

@@

## looking at noninformative vs. informative (cubic)
dplyr::select(res_covset, Method, setting, dist, key, mean_value, se) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("TPR"),
                  ! Method %in% c("ashq", "bonf")) %>%
    dplyr::mutate(plus1se = mean_value + se, minus1se = mean_value - se) %>%
    dplyr::select(-se) %>%
    tidyr::gather(metric, value, mean_value, plus1se, minus1se) %>%
    tidyr::unite(metric, c("setting", "metric")) %>%
    tidyr::spread(metric, value) %>%
    ggplot(aes(x = noninformative_mean_value, y = `informative-cubic_mean_value`, color = Method)) +
    geom_errorbar(aes(ymin = `informative-cubic_minus1se`, ymax = `informative-cubic_plus1se`), width = 0) +
    geom_errorbarh(aes(xmin = noninformative_minus1se, xmax = noninformative_plus1se), height = 0) + 
    ##geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 1, scales = "free", labeller = labeller(dist = label_parsed)) +
    scale_x_continuous(labels = scales::percent) + 
    scale_y_continuous(labels = scales::percent) + 
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    ggtitle("Mean TPR for Informative and Noninformative Simulations") 
```

@@

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(pfdr + guides(color = FALSE, linetype = FALSE), ptpr,
                rel_widths = c(1, 1.4), labels = LETTERS[1:2])
gp

@@

## not including SE because it's too small
pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "FDR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    ##geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), alpha = 1) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Null Proportion")

## not including SE because it's too small
ptpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    ##geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), alpha = 1) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average TPR Across Varying Null Proportion")
```

@@

## We don't include the error bars because the SEs are so small
uniplot <- dplyr::select(res_unimodal, Method, dist, signal, key, mean_value, se, col, lty) %>%
    dplyr::filter(key %in% c("FDR", "TPR")) %>%
    dplyr::mutate(plus1se = mean_value + se, minus1se = mean_value - se) %>%
    dplyr::select(-se) %>%
    tidyr::gather(metric, value, mean_value, plus1se, minus1se) %>%
    tidyr::unite(metric, c("key", "metric")) %>%
    tidyr::spread(metric, value) %>%
    ggplot(aes(x = TPR_mean_value, y = FDR_mean_value, color = Method)) +
    ##geom_errorbar(aes(ymin = FDR_minus1se, ymax = FDR_plus1se), width = 0) +
    ##geom_errorbarh(aes(xmin = TPR_minus1se, xmax = TPR_plus1se), height = 0) + 
    geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("TPR", labels = scales::percent, breaks = seq(0, 1, .2)) + 
    scale_y_continuous("FDR", labels = scales::percent, breaks = seq(0, 1, .2)) + 
    facet_grid(signal ~ dist, labeller = labeller(dist = label_parsed)) + 
    ggtitle("Average FDR and TPR Across Unimodal Settings")
uniplot

@@

## not including SE because it's too small
pfdr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, se, q10, q90, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    ##geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Informativeness")
pfdr

ptpr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    ##geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0) +    
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ ., scales = "free_y") + expand_limits(y = 0) +
    ggtitle("Average TPR Across Varying Informativeness")
ptpr
```
